### 2022-02-09 symposium.tex
Type and Null Safety for Regexes

The term-level component of our library is in charge of sanitizing and packaging the results of regular expression matchings.
Concretely, this component's job consists in transforming the string array that comes out of the regex engine into an appropriately sized tuple, with nullable elements wrapped in options.
That transformation must conform to the representation computed at the type level.

@@

This solution has the benefit of being conceptually simple.
We needed to write an implementation that conforms to our type-level program, and we did!
By duplicating that program, and using an unsafe case to convince the compiler of our good intentions.

@@

In principle, Scala~3's type inference should be able to solve half of the problem with its ability to correlate match types and match expression.
In \Cref{subsec:a-lightweight-form-of-dependent-typing}, we show an example of that ability, where the compiler type checks a small program using a match type.
In our case, this mechanism should allow us to get rid of the unsafe cast but does not address the problem of code duplication.
In practice, at the time of writing, this solution does not play well with predefined types from the standard library, because the compiler lacks the knowledge necessary to correlate those types with their term-level counterpart.
For instance, the compiler does not recognize |CharAt["foo",0]| as a valid type for |"foo".chatAt(0)|.

>>>>

The term-level component of our library is in charge of sanitizing and packaging the results of regular expression matchings.
Concretely, this component's job consists of transforming the string array that comes out of the regex engine into an appropriately sized tuple, with nullable elements wrapped in options.
That transformation must conform to the representation computed at the type level.

@@

This solution has the benefit of being conceptually simple.
We needed to write an implementation that conforms to our type-level program, and we did!XXX
By duplicating that program, and using an unsafe cast to convince the compiler of our good intentions.

@@

In principle, Scala~3's type inference should be able to solve half of the problem with its ability to correlate match types and match expressions.
In \Cref{subsec:a-lightweight-form-of-dependent-typing}, we show an example of that ability, where the compiler type checks a small program using a match type.
In our case, this mechanism should allow us to get rid of the unsafe cast but does not address the problem of code duplication.
In practice, at the time of writing, this solution does not play well with predefined types from the standard library, because the compiler lacks the knowledge necessary to correlate those types with their term-level counterpart.
For instance, the compiler does not recognize |CharAt["foo",0]| as a valid type for |"foo".chatAt(0)|.
